### 2022-09-12 paper/writeup.tex
Update writeup.tex
some changes

\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\P}{\mathbb{P}}

@@

@@

% (ADAM)
% * reduction in edges ~ sequence length
% * speed increase ~ sequence length
% * proprotion of added edges that are true ~ sequeence length
% * apply to real data:
%     - % fewer edges
%     - % fewer distinct ancestors (ancestral paths?) of sample at some time

>>>>

\documentclass{article}
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{natbib}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{tikz, tikzcd}

\newcommand{\E}{\mathbb{E}}
\renewcommand{\P}{\mathbb{P}}
\newcommand{\R}{\mathbb{R}}

@@

\begin{section*}{Notation}
    We begin with some notation. We define a \textit{tree sequence}, denoted $TS$, 
    as a tuple $\left\( \left\{T_k\right\}, N, E, L\right\)$ where
     $\left\{T_k\right\}_{k=1}^n is the set of trees,
     $N$ and $E$ are the sets of nodes and edges respecitively,
     and $L=[0,a)\subseteq \R$ is the length of the sequence on the genome. 
    Additionally, a node $x\in N$ is \textit{unary} if it only has one child, 
    ie. only a single edge extending below it on the tree.
    With these tree sequences our goal is to
    minimize the number of edges
    as well as infer coalescence of genes. 
    To remove edges we consider the following example.
    Suppose for a tree $T_k$ in the tree sequence $TS$ 
    there exists a branch which contains a unary node $b\in N$.
    Then the node $b$ has one parent, $a\in N$, 
    and one child $c\in N$,
    each with edges $e_{ab}, e_{bc}\in E$ connecting them.
    If there is an edge between the nodes $a$ and $c$ in trees 
    $T_{k+1} (or $T_{k-1}$),
    then we wish to extend the edges $e_{ab},e_{bc}$ 
    to $T_{k+1}$ and then remove the edge $e_{ac}$ from $T_{k+1}. 
    This action reduces the length of the edge $e_{ac}$ on the genome,
    and in some cases, completely removes the edge. 
    We now perfrom this action on all such unary nodes 
    over the entire tree sequence.

    In full detail, let $TS = \left\( \left\{T_k\right\}_{k=1}^n, N, E, L\right\)
    be a tree sequence.

\begin{algorithm}
\caption{Extend Edges}\label{alg:cap}
\begin{algorithmic}
    N' <- N
    e'\in E' <- 
    T'_k <- T_{n-k}
    T' <- (\{T'_k\}_{k=1}^n,N',E',L)

\end{algorithmic}
\end{algorithm}

@@

% (AVA)
% * reduction in edges ~ sequence length
% * speed increase ~ sequence length
% * proprotion of added edges that are true ~ sequeence length
% * apply to real data:
%     - % fewer edges
%     - % fewer distinct ancestors (ancestral paths?) of sample at some time
